The \dealii Library, Version 9.6

### 2024-09-17 9.6/paper.tex
Fix some typos

The major changes of this release are:
%
\begin{itemize}
  \item Substantial improvements to the multigrid two-level transfer
    operators, including matrix-free based versions and versions for
    p-refinement (Section~\ref{sec:mf}).
  \item Different additions to the non-matching infrastructure (see
    Section~\ref{sec:nonmatching}). In particular, the new class
    FERemoteEvaluation provides support for evaluating
    finite element shape functions and solutions on parts of the
    domain stored by other MPI processes.
  \item Much work has gone into writing wrappers for Trilinos' Tpetra
    stack of linear algebra classes. Tpetra is Trilinos' Kokkos-based
    replacement for the now-deprecated Epetra stack. See
    Section~\ref{sec:tpetra} for more on this.
  \item Tool classes \texttt{TaskResult} and \texttt{Lazy} that provide ways to compute
    values on a separate thread or only when first accessed (Section~\ref{sec:tools}).
  \item There are six new tutorial programs, on checkpointing simulations
    (step-83), integrating time-dependent solvers with external time
    stepping libraries (step-86, using PETSc's TS library), advanced
    point evaluation techniques (step-87), non-matching grids
    (step-89), and trace-based methods for PDEs on embedded surfaces
    (step-90). See Section~\ref{subsec:steps} for more details.
\end{itemize}
%

@@

We made different updates to the matrix-free infrastructure in \dealii. These include:
\begin{itemize}
\item Our own implementation of \texttt{std::simd} (\texttt{VectorizedArray}) now
  also Arm Neon. Arm Neon is an architecture extension for
  the Arm Cortex-A and Arm Cortex-R series of processors, commonly used in Apple
  products. With these instructions 2 doubles or 4 floats can be processed in one
  go. Since matrix-free infrastructure works directly with \texttt{VectorizedArray}
  data structures, it automatically benefits from this extension.

>>>>

The major changes of this release are:
%
\begin{itemize}
  \item Substantial performance improvements to the matrix-free and multigrid
   infrastructure (Section~\ref{sec:mf}).
  \item Different additions to the non-matching infrastructure (see
    Section~\ref{sec:nonmatching}). In particular, the new class
    FERemoteEvaluation provides support for evaluating
    finite element shape functions and solutions on parts of the
    domain stored by other MPI processes.
  \item Much work has gone into writing wrappers for Trilinos' Tpetra
    stack of linear algebra classes. Tpetra is Trilinos' Kokkos-based
    replacement for the now-deprecated Epetra stack. See
    Section~\ref{sec:tpetra} for more on this.
  \item Tool classes \texttt{TaskResult} and \texttt{Lazy} that provide ways to compute
    values on a separate thread or only when first accessed (Section~\ref{sec:tools}).
  \item There are six new tutorial programs, on checkpointing simulations
    (step-83), integrating time-dependent solvers with external time
    stepping libraries (step-86, using PETSc's TS library), advanced
    point evaluation techniques (step-87), non-matching grids
    (step-89), and trace-based methods for PDEs on embedded surfaces
    (step-90). See Section~\ref{subsec:steps} for more details.
\end{itemize}
%

@@

We made different updates to the matrix-free infrastructure in \dealii. These include:
\begin{itemize}
\item Our own implementation of \texttt{std::simd} (\texttt{VectorizedArray}) now
  also supports Arm Neon. Arm Neon is an architecture extension for
  the Arm Cortex-A and Arm Cortex-R series of processors, commonly used in Apple
  products. With these instructions 2 doubles or 4 floats can be processed in one
  go. Since matrix-free infrastructure works directly with \texttt{VectorizedArray}
  data structures, it automatically benefits from this implementation extension.
